Double Trouble: Understanding Sex Differences in Synthetic Lethal interactions in Human Cancers \\~\\ Project Updates

### 2023-07-15 july18meeting_pres2/may30ccgmeeting.tex
updates

@@

	\begin{frame}
		content...
	\end{frame}

>>>>

	\begin{frame}{DE Genes Found in Males and Females are Enriched in Cancer-Related Processes}
		\includegraphics[width=11cm, height=7cm]{all_cancersgsea_inbothdegenes_male_female_bp0.9.png}
	\end{frame}

@@

	\section{Synthetic Lethality}
	\begin{frame}{Using DE Genes to Find Sex-Specific Synthetic Lethal Pairs}
		content...
	\end{frame}

	\section{Supplementary Slides}
	\begin{frame}{Supplementary 1 - Histogram Showing Normalization}
		\includegraphics[width=12cm, height=7cm]{all_cancers-F_before_and_after_normalization_hist.png}
	\end{frame}

	\begin{frame}{Supplementary 2 - Gene Expression Across Tissues}
		content...
	\end{frame}
